

% Is it possible to keep my translation together with original text?
% https://tex.stackexchange.com/questions/5076/is-it-possible-to-keep-my-translation-together-with-original-text
\chapter{\lang{Theory base}{Fundamentação Teórica}}


\section{\lang{What does coding is}{Programação de computadores}}

\lang{
    Coding is like writing and reading a book for the large people, you like it
    to look beautifully. Or at least do you expect such when you buy a book, for
    example, to learn programming for you first time \cite{howNovicesRead}.
    You expect:
    \begin{enumerate}
        \item
            Things to be well organized,
            so you do not get lost.
        \item
            The colors to be properly placed,
            so you do not get distracted from the main content.
        \item
            The spacing between paragraphs, words, chapters, sections
            subsections, etc, to be well adjusted.
            Not everything cluttered in only one file,
            line, function, class, or whatsoever so.
    \end{enumerate}
}{%
    Programar pode ser considerado pela maioria das pessoas como escrever um livro,
    e para tal,
    gostar~=se mais caso este ``livro'' tenha uma boa aparência.
    No mínimo espera~=se algumas características chave ao comprar~=se
    um livro \cite{visualizationsInAFunctionalProgramming}.
    Por exemplo,
    quando compra~=se um livro para aprender a programar pela primeira vez,
    espera-se que \cite{howNovicesRead}:
    \begin{enumerate}
        \item
            Seu conteúdo esteja bem organizado,
            para que o leitor não perda-se durante sua leitura.
        \item
            Que suas cores estejam propriamente escolhidas e
            utilizadas,
            para que elas não distraiam o leitor ou tirem o foco do principal,
            o conteúdo do livro.
        \item
            Que o espaçamento entre os parágrafos,
            palavras, capítulos, seções, subseções, etc, estejam propriamente ajustados,
            e não todo aglomerado ou desordenado em um único parágrafo,
            frase, capítulo,
            etc.
    \end{enumerate}
}

\advisor{}{%
    \subsection{\lang{Computer Assisted Programming}{Programação auxiliada}}

    \lang{%
        Your computer should help you with these unforeseen tasks.
        Why should I spend my precious time checking whether I am actually copying
        something space indented,
        when I am actually coping something tab indented?
        Perhaps we should sit and cry while waiting for some greater force to come
        and rescue us. Or may be you should stop crying and actually do something
        about other than keep waiting for you mommy to come and save you from the
        darkness growing behind you back leading you to endless unsleepy nights
        fixing your code just because everything just went wrong.
    }{%
        Seu computador deveria ajudar você com aquelas imprevistas tarefas.
        Por que eu deveria gastar meu precioso tempo verificando se algo que estou copiando,
        está indentado por ``TAB''\s ou espaços?
        Talvez devêssemos sentar e
        chorar enquanto aguardamos que alguma força maior do Universo venha e
        nos salve.
        Ou talvez você deva para de chorar e
        realmente fazer alguma coisa a respeito além de continuar esperando que sua mamãe venha e
        resgate você da escuridão crescendo pela suas costas levando você a infinitas noites
        acordado corrigindo seu código simplesmente por que tudo deu errado.
    }
}

% \section{Gramáticas}

% O que são Gramáticas?


% \subsection{Expressões Regulares}

% O que são Gramáticas?


% \subsection{Gramáticas Livre de Contexto}


% \subsection{Sintaxes de linguagens}

% O que são sintaxes de linguagens?


\subsection{Tradução de Código}

\lang{%
    This work aims to propose a translator \cite{generatingInterpretiveTranslators},
    where the input and output languages are the same language.
    Such translation objective is to change the language representational structure,
    but without affecting the language lex,
    syntactic or semantics, i.e.,
    the language meaning.

    This program class is commonly know as text formatters.
    The differential from this work from others is the goal of a single expandable tool,
    capable of manipulating all existent and future programming languages,
    based on the use of deterministic \cite{introductionToContextFreeGrammars}
    and controlled nondeterministic
    % \cite{TODO:section explaning what does controlled means}
    context free grammars.
}{%
    Em linguagens formais,
    tradutores são ferramentas que operam realizando a transformação de um programa de entrada,
    em um programa de saída \cite{generatingInterpretiveTranslators}.
    Diferente de um compilador,
    a linguagem de destino da ``tradução'' é do \textbf{mesmo nível} que a linguagem de origem.
    Por exemplo,
    dado a aplicação um programa de entrada em C++ e
    a saída de um programa em Java,
    tem-se um processo de tradução.
    Pelo outro lado,
    dado um programa de entrada em C++ e
    um programa de saída em Assembly,
    tem-se um processo de compilação \cite{translatorGenerationCompilier}.
}

\subsection{Formatadores de código}

Também conhecidos como embelezadores\footnote{do inglês:
Beautifiers} \cite{prettyPrintingForSoftware} de código,
``pretty~=printing'' tem o mesmo significado que beautifying.

    A robust Code Beautifier can get a lot more complicated just with the basic
    definitions of formatting (\nameref{source_code_beautifiers})
    applied over each language own characteristics
    as for example:

\begin{enumerate}[nosep,nolistsep]
    \item
        Add spaces before if\s name as in `if(var)' versus `if (var)'
    \item
        Add spaces inside if\s as in `if(var)' versus `if( var )'
    \item
        Add spaces before for\s name as in `for(var)' versus `for (var)'
    \item
        Add spaces inside for\s as in `for(var)' versus `for( var )'
\end{enumerate}

    As may be noticed, the list may became quite big,
    and if fact such big list of rules has been implemented.
    Looking over the Beautifier called
    `Uncrustify'\footnote{\url{https://github.com/uncrustify/uncrustify}},
    we can find about 500 settings with specifications like these above.

    The problem about is, even if you go through all these settings,
    which will take you quite some time,
    you still only configuring a few languages closely related.
    On this case, C, C++, Java, Pawn, etc.
    For all other languages you still need to find out another source code
    formatter tool, which will be certainly
    limited\footnote{\url{https://stackoverflow.com/questions/31438377/how-can-i-get-eclipse-to-wrap-lines-after-a-period-instead-of-before}}
    and still need to configure all over again.

